---
title: "TASK 2"
output: html_notebook
---

# Cake ingredients Analysis

## import libraries
```{r}
library(tidyverse)
library(here)
```

## import cleaned data
```{r}
clean_cake_data <- read_csv(here("data/clean_data/cake_data_clean.csv"))
```


### Which cake has the most cocoa in it?
```{r}
clean_cake_data %>% 
  filter(ingredient == "cocoa") %>% 
  slice_max(quantity) %>% 
  select(cake) %>% 
  pull()
```
#### However In general, a 1-ounce piece of unsweetened chocolate can replace 3 Tbsp
```{r}
#However In general, a 1-ounce piece of unsweetened chocolate can replace 3 Tbsp
cocoa_contents <- clean_cake_data %>% 
  filter(ingredient %in% c("cocoa","chocolate")) %>% 
  mutate(tbsp_eqiv = case_when(
    ingredient == "chocolate" ~ quantity*3,
    TRUE ~ quantity
  ))
  
cocoa_contents %>% 
  slice_max(tbsp_eqiv) %>% 
  select(cake) %>% 
  pull()
```


### For sponge cake, how many cups of ingredients are used in total?
```{r}
sponge_cups_req <- clean_cake_data %>% 
  filter(cake == "Sponge" & measure == "cup") %>% 
  summarise(sum(quantity)) %>% 
  pull()
```

### How many ingredients are measured in teaspoons?
```{r}
ingredients_teaspoons <- clean_cake_data %>% 
  filter(measure == "teaspoon") %>% 
  distinct(ingredient) %>% 
  count() %>% 
  pull()
```

### Which cake has the most unique ingredients?
```{r}
clean_cake_data %>% 
  group_by(cake) %>% 
  tally() %>% 
  arrange(desc(n)) %>% 
  slice_max(n)
```

### Which ingredients are used only once?
```{r}
clean_cake_data %>% 
  count(ingredient) %>% 
  slice_min(n) %>% 
  select(ingredient) %>% 
  pull()
```

