---
title: "TASK 1"
output: html_notebook
---

# Decathlon Data Analysis


## import libraries
```{r}
library(tidyverse)
library(here)
```


## load cleaned data
```{r}
decathalon_data <- read_csv(here("data/clean_data/decathlon_clean.csv"))
```


### Who had the longest long jump seen in the data?
```{r}
decathalon_data %>% 
  select(!points) %>% 
  filter(event == 'long_jump') %>%
  slice_max(distance_or_time, n = 1)
```


### What was the average 100m time in each competition?
```{r}
decathalon_data %>%
  group_by(competition) %>% 
  filter(event == 'x100m') %>%
  summarise(average_100m = mean(distance_or_time))
```

    
### Who had the highest total points across both competitions?
```{r}
decathalon_data %>% 
  select(!(event|distance_or_time)) %>% 
  unique() %>% 
  group_by(name) %>% 
  summarise(total_points = sum(points)) %>% 
  arrange(desc(total_points)) %>%
  slice(1)
```


### What was the shot-put scores for the top three competitors in each competition?
```{r}
decathalon_data %>%
  filter(event == "shot_put") %>% 
  group_by(competition) %>% 
  arrange(desc(distance_or_time)) %>% 
  slice_head(n = 3)

decathalon_data %>%
  filter(event == "shot_put") %>% 
  group_by(competition) %>% 
  slice_max(distance_or_time, n = 3)
```


### What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?
```{r}
fastest_runner_400m <- decathalon_data %>% 
  filter(event == "x400m" & distance_or_time < 50)

slowest_runner_400m <- decathalon_data %>% 
  filter(event == "x400m" & distance_or_time > 50)
```

```{r}
fastest_400_avg <- fastest_runner_400m %>% 
  summarise(avg_points = mean(points)) %>% 
  pull()

slowest_400_avg <- slowest_runner_400m %>% 
  summarise(avg_points = mean(points)) %>% 
  pull()
```


