---
title: "TASK 4"
output: html_notebook
---

# Halloween Candy Data Analysis

## import libraries
```{r}
library(tidyverse)
```

## import cleaned data
```{r}
candy_data <- read_csv("data/clean_data/candy_data_clean.csv")
```

### What is the total number of candy ratings given across the three years. (Number of candy ratings, not the number of raters. Don’t count missing values)
```{r}
num_rating <- candy_data %>% 
  filter(!is.na(rating)) %>%
  count() %>% 
  pull()

num_rating
```

### What was the average age of people who are going out trick or treating?
```{r}
avg_age_going_out <- candy_data %>% 
  filter(going_trick_or_treating == "Yes" & !is.na(age)) %>% 
  group_by(id) %>%
  slice(1) %>% 
  ungroup() %>% 
  summarise(average_age = mean(age, na.rm = TRUE)) %>% 
  pull()

avg_age_going_out
```

### What was the average age of people who are not going trick or treating?
```{r}
avg_age_not_going_out <- candy_data %>% 
  filter(going_trick_or_treating == "No" & !is.na(age)) %>% 
  group_by(id) %>%
  slice(1) %>% 
  ungroup() %>% 
  summarise(average_age = mean(age, na.rm = TRUE)) %>% 
  pull()

avg_age_not_going_out
```

### For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}
candy_data %>% 
  group_by(rating, candy) %>% 
  summarise(n_ratings = n()) %>% 
  slice_max(n_ratings) %>% 
  head(3)
```

```{r}
#check top joY
candy_data %>% 
  filter(rating == "JOY") %>% 
  group_by(rating, candy) %>% 
  summarise(n_ratings = n()) %>% 
  slice_max(n_ratings)
```


```{r}
#check top despair
candy_data %>% 
  filter(rating == "DESPAIR") %>% 
  group_by(rating, candy) %>% 
  summarise(n_ratings = n()) %>% 
  slice_max(n_ratings)
```

```{r}
#check top MEH
candy_data %>% 
  filter(rating == "MEH") %>% 
  group_by(rating, candy) %>% 
  summarise(n_ratings = n()) %>% 
  slice_max(n_ratings)
```

### How many people rated Starburst as despair?
```{r}
starburst_despair <- candy_data %>% 
  filter(rating == "DESPAIR" & candy == "starburst") %>% 
  count() %>% 
  pull()
```


#For the next three questions, count despair as -1, joy as +1, and meh as 0.

### What was the most popular candy bar by this rating system for each gender in the dataset ?
```{r}
candy_data %>% 
  mutate(rating = case_when(
    rating == "JOY" ~ 1,
    rating == "DESPAIR" ~ -1,
    TRUE ~ 0
  )) %>% 
  group_by(gender, candy) %>%
  summarise(score = sum(rating)) %>% 
  slice_max(score, n = 2)
```


### What was the most popular candy bar in each year?
```{r}
candy_data %>% 
    mutate(rating = case_when(
    rating == "JOY" ~ 1,
    rating == "DESPAIR" ~ -1,
    TRUE ~ 0
  )) %>% 
  group_by(year, candy) %>% 
  summarise(score = sum(rating)) %>% 
  slice_max(score, n = 2)
```


### What was the most popular candy bar by this rating for people in US, Canada, UK, and all other countries?
```{r}
candy_data %>% 
    filter(!is.na(country)) %>% 
    mutate(rating = case_when(
    rating == "JOY" ~ 1,
    rating == "DESPAIR" ~ -1,
    TRUE ~ 0
  )) %>% 
  group_by(country, candy) %>% 
  summarise(score = sum(rating)) %>% 
  slice_max(score, n = 2, with_ties = FALSE)
```

